\chapter{Router Configuration}
\section{Static Routing}
Static routing is a method of explicitly stating where a router should send its
traffic for a given network. Due to its administrative distance of 1, a static
route is chosen over any other routing protocol, only being overruled if the
router can see that the destination address is on a local interface (directly
connected). Once our network began to adopt IS-IS as its interior gateway
protocol (IGP) static routes were removed in favor of dynamic routing. They
were also removed from the configurations to ensure that static routes were not
erroneously chosen over an IS-IS sourced counterpart.

\begin{lstlisting}[caption={Alpha Static Route}, label={listing:alpha-static}]
ip route 10.1.1.1 255.255.255.255 100.100.105.1
\end{lstlisting}

In the final topology of our network a single static route remained in use, the
configuration of which is shown in Listing~\ref{listing:alpha-static}. This
route was used as a component of the eBGP peer link to Autonomous System No.
42. The peering was sourced from a loopback interface on the remote side and
    because of this the local side required a static route which provided
    initial connectivity to the loopback. Without the use of these static
    routes the BGP sources on both sides would not have been able to
    communicate and thus would never have peered with one another.

\section{Interior Gateway Protocols (IGP)}
Within the three-router layout, it can be seen that all networks in the topology
have at least two paths to connect them to any other network. Because of this
it was decided that the use of static routing would not provide the fault
tolerance that would be expected of an ISP network. Instead we opted to use an
IGP to provide automatic routing within our infrastructure. This was done using
Intermediate System - Intermediate System (IS-IS), a link state protocol which
computes the shortest path between devices in the network using Dijkstra's
Shortest Path Algorithm. We opted to use dynamic routing in our internal
infrastructure due to their reliability and fast convergence time when any
issues arise within their networks.

IS-IS was implemented using the loopback interfaces defined on each router in
the network. From the IP address of these loopbacks, we have defined a NET
address which represents the device in the IS-IS routing process. The NET is in
NSAP format which defines information about the device such as its Area ID and
a unique ID to identify it within that area. An example NET address for Alpha
is shown in Listing~\ref{listing:alpha-isis}. From this we can see that Alpha
was a member of Area 1 and had an IP address of \texttt{12.1.1.1}.

\begin{lstlisting}[caption={Alpha IS-IS Configuration}, label={listing:alpha-isis}]
hostname Alpha
!
router isis
 net 49.0001.0120.0100.1001.00
 is-type level-1
 passive-interface FastEthernet0/0/1
\end{lstlisting}

For IS-IS to include networks in its routing table, each network also needs to be
added on an interface-by-interface basis, flagging the interface to be included
in the routing table. This was implemented on all interfaces inside of our ISP
for both IPv4 and IPv6. Once both the routing process and the interfaces for
routing have been defined on all devices, the IS-IS process runs the shortest
path algorithm and selects the best routes within its network. When connecting
to other Autonomous Systems for BGP, it soon became apparent that other groups
had opted for a similar NET address schema to ourselves. This caused additional
problems as routes from another ISP's IS-IS process were being passed into our
infrastructure. In order to stop these routes from coming into the internal
routing process, passive interfaces were configured on all external links. This
allowed the interface to remain in the IS-IS routing table and prevented route
updates from being sent or received on that link.

\section{Exterior Gateway Protocols}
In order for our ISP to provide internet access to our customers, we needed to have
a complete internet routing table from which we could identify the best
possible routes for our customers' traffic to reach its destination. In
addition to having knowledge of an internet routing table, we also had to
provide alternate paths to a destination if a route went offline or links
became saturated with network traffic. In order to provide both of these
services we had to use an EGP, of which the only option currently in use is the
Border Gateway Protocol (BGP). This external routing protocol allows autonomous
systems to interact with one another through the exchange of prefixes (network
advertisements) or through traffic management in the form of BGP policy.

The implementation of BGP can be further broken down into two separate forms,
eBGP and iBGP. The first of these handles the peering and advertisements
between autonomous systems, facilitating the distribution of the BGP prefix
table and the configuration of routing metrics on these prefixes in order to
influence routing decisions. In comparison, the iBGP process handles the
propagation of the prefix table throughout internal routers.

For our ISP's peering to other ISPs, we opted to take the approach of peering
with the source of a loopback interface rather than the traditional method of
using the source interface of the connection. This decision was taken at an
early stage of the BGP peering process with the intention of introducing
redundant connections to peers or implementing multi-hop peering to other
autonomous systems. However these plans were not implemented due to a lack of
time and physical interfaces on some routers. Implementation of these
connections would have required additional configuration on our peers' networks
as they would need to have configured a static route on their device in order
to connect to our loopback and begin the peering process. A snippet of our
neighbour peering configuration is shown in Listing~\ref{listing:sky-ebgp-conf}.
It can be seen that in addition to updating the source of the BGP
process, it was also necessary to add the command \texttt{disable-connected-
check} which removed a test for BGP peers to ensure that they were directly
connected. However from our experience in the lab, we found that this command
alone did not allow a peering to form. The additional command \texttt{ebgp-multihop 2}
was also required in order for the peers to form correctly.

\begin{lstlisting}[caption={BT-Sky eBGP Configuration}, label={listing:sky-ebgp-conf}]
router bgp 2110
!
! Omitted
!
 neighbor 12.11.0.2 remote-as 5607
 neighbor 12.11.0.2 description PEER_TO_GROUP1
 neighbor 12.11.0.2 ebgp-multihop 2
 neighbor 12.11.0.2 disable-connected-check
 neighbor 12.11.0.2 update-source Loopback0
!
\end{lstlisting}

All three routers in the topology were configured to distribute their eBGP
routes to one-another through iBGP. These internal peers were again formed on
loopback addresses as a countermeasure for link failure between the routers
tearing down peer relationships. The use of a loopback allows the peering to
remain up after IS-IS converges, in comparison using the interface address
would cause the peering to fail as the IP address would not be reachable after
a link failure. The command \texttt{next-hop-self} was used to tell the local
iBGP process to label any routes with their own address as the next hop.
Without this command the next-hop on any routes would have remained as the next-
hop for the sending router and this would have caused connectivity issues. A
snippet of the iBGP peering configuration between Bravo and Alpha is shown in
Listing~\ref{listing:bravo-ibgp-conf}

\begin{lstlisting}[caption={Bravo-Alpha iBGP Configuration}, label={listing:bravo-ibgp-conf}]
router bgp 2110
 neighbor 12.1.1.1 remote-as 2110
 neighbor 12.1.1.1 update-source Loopback0
 neighbor 12.1.1.1 next-hop-self
\end{lstlisting}

The contents of the prefix table that was distributed by our AS was dependent
on the configured network statements under the BGP process. This allowed us to
dictate which of our local networks we wanted our peers to know about and
therefore allow their traffic to reach. In our configurations, we decided that
the prefixes we sent should be as specific as possible and should not advertise
unnecessary sections of our network, such as internal point-to-point links.
From this decision we were able to narrow the advertised networks down to a
list of six unique prefixes which were in two groups: the
Customer Segment networks which housed webservers, DNS and our customers and 
our router subnets, which would facilitate eBGP multihop
peers as discussed earlier. The configuration for these network advertisements
is shown in Listing~\ref{listing:bravo-net-conf}.

\begin{lstlisting}[caption={Bravo BGP Network Configuration}, label={listing:bravo-net-conf}]
router bgp 2110
 network 12.0.1.0 mask 255.255.255.0
 network 12.0.2.0 mask 255.255.255.0
 network 12.0.3.0 mask 255.255.255.0
 network 12.1.1.1 mask 255.255.255.255
 network 12.2.2.2 mask 255.255.255.255
 network 12.3.3.3 mask 255.255.255.255
\end{lstlisting}

\section{Security}
Our first security measure was having a user account for every router
and laptop in our setup. For ease of use all users were called ``group2''. This
added the first layer of security, meaning a password was required to access
the devices.

For routers, a second ``enable'' password was enforced. This prevented unauthorised users
from entering enable mode on the routers and was set with the command
\texttt{enable password \#\#\#\#\#}. The command
\texttt{service~password-encryption} was then used to encrypt the passwords so
they did not appear in the router configuration files as plaintext. It should
be noted that
\texttt{service password-encryption} uses a weak form of
encryption~\cite{ciscocracker}, and so is best used only as a deterrent for
issues like shoulder-surfing. The alternate option would have been to use
\texttt{enable secret \#\#\#\#\#} instead which stores the password as an MD5
hash. However seeing as MD5 is fairly weak anyway~\cite{md5} we didn't feel it
would make much difference.

Additionally, telnet was also disabled over router VTY lines. This was done
because telnet sends login information in plaintext, and so is inherently
insecure. Instead we used SSH with RSA keys to allow secure passwordless
access. Note that this only made SSH authentication passwordless, both router
passwords remained in place.

\section{Traffic Management}
In order to simulate a real world situation, traffic entering and leaving our
network needed to be managed. To demonstrate this, AS 42 was setup to
be our provider, whilst DT and Sky were setup as peers to our ISP.

As our provider, AS 42 should have been able to see routes to our network and to
our peers' networks. In order to do this, our prefix (\texttt {12.0.0.0/8}) and
our peers' prefixes, \texttt{8.0.0.0/8} (Sky) and
\texttt{34.0.0.0/8} (DT), were advertised to it.

In order to perform this filter, an access list (Listing~\ref{listing:alpha-access})
was defined on Alpha to match
all routes that did not belong to the prefix of \texttt{10.0.0.0/8}, i.e.
routes not local to AS 42. A route map (Listing~\ref{listing:alpha-route-map}) was then used to tag these routes with
the well known community tag no-export. This stopped the router from
advertising routes to anything that was not on our provider's network.

\begin{lstlisting}[caption={Alpha Access List}, label={listing:alpha-access}]
ip access-list standard MATCH_NONPEER
 deny   10.0.0.0 0.255.255.255
 permit any
\end{lstlisting}
\begin{lstlisting}[caption={Alpha Route Map}, label={listing:alpha-route-map}]
route-map PEER_NOEXPORT permit 10
 match ip address MATCH_NONPEER
 set community no-export
\end{lstlisting}

As Sky and DT were setup to act as peers to our ISP, they should have been able to
access our network but should not have been able to access each other through us. However,
for the sake of providing our peers with redundancy if their link to AS 42 was
disrupted, we allowed them to access our provider through our network. In order
for this to work, only the \texttt{10.0.0.0/8} and \texttt{12.0.0.0/8} prefixes
were advertised to our peers. This allowed the peers to see routes to our
network and AS 42, but not each other.

Access lists similar to Alpha were defined on Bravo and Charlie in order to
only advertise prefixes to routes local to our peers. Bravo was connected to
Sky, so routes not on the \texttt{8.0.0.0/8} prefix were tagged with the
community tag no-export. Charlie was connected to DT, so it tagged routes not
on the \texttt{34.0.0.0/8} prefix with the community tag no-export. As our
peers were not allowed to communicate with each other through us, we also had
to define prefix lists (Listing~\ref{listing:bravo-charlie-prefix-list}) on Bravo and Charlie. As they were both allowed to
access our network and our provider, prefix lists were created to permit the
\texttt{10.0.0.0/8} to \texttt{10.0.0.0/32} prefixes and the
\texttt{12.0.0.0/8} to \texttt{12.0.0.0/32} prefixes. This set the routers to
only advertise our network and our provider's network to our peers.

\begin{lstlisting}[caption={Bravo and Charlie Prefix List}, label={listing:bravo-charlie-prefix-list}]
ip prefix-list OUT_PEER_ROUTES seq 5 permit 10.0.0.0/8 le 32
ip prefix-list OUT_PEER_ROUTES seq 10 permit 12.0.0.0/8 le 32
\end{lstlisting}

In summary:

\begin{itemize}
    \item Alpha advertised all prefixes to routes local to our provider
    (\texttt{10.0.0.0/8})

    \item Bravo advertised our prefixes (\texttt{12.0.0.0/8} to \texttt
    {12.0.0.0/32}) and our provider's prefixes (\texttt{10.0.0.0/8} to
    \texttt{10.0.0.0/32}) to routes local to Sky (\texttt{8.0.0.0/8})

    \item Charlie advertised our prefixes (\texttt{12.0.0.0/8} to \texttt
    {12.0.0.0/32}) and our provider's prefixes (\texttt{10.0.0.0/8} to \texttt
    {10.0.0.0/32}) to routes local to DT (\texttt{34.0.0.0/8})
\end{itemize}
